Insert the article title here

### 2020-07-23 tex/results.tex
Finally got the table to work

THIS ARE THE PEAKS OF FIGURE \ref{fig:AR_22_vs_norm} need to find a better way of 
present these numbers.

AR 1 peaks at frequency\\
normal: [ {\color{green}917.73} 934.092 949.604 957.325]\\
22 deg: [ {\color{red}883.926} {\color{green}917.73} 935.052 949.604 957.325]\\

AR 2 peaks at frequency\\
normal: [ {\color{green}903.233} 926.395 944.762 958.242]\\
22 deg: [ {\color{red}896.517} {\color{green}903.233} 926.395 944.762 958.242]\\

AR 3 peaks at frequency\\
normal: [ {\color{green}888.793} 922.552 931.223 948.613 958.242]\\
22 deg: [ {\color{green}888.793} 899.418 922.552 931.223 958.242]\\

AR 4 peaks at frequency\\
normal: [ {\color{green}876.186} 929.32 946.639 958.242]\\
22 deg: [ {\color{green}876.186} 901.281 921.618 929.32 945.745 958.242]\\

AR 5 peaks at frequency\\
normal: [ {\color{green}865.576} 926.395 945.745 958.242]\\
22 deg: [ {\color{green}865.576} 901.281 921.618 958.242]\\

AR 6 peaks at frequency\\
normal: [ {\color{green}856.904} 914.793 923.489 929.32 946.639 958.242]\\
22 deg: [ {\color{green}856.904} 901.281 920.6 958.242]\\

AR 7 peaks at frequency
normal: [ {\color{green}850.134} 910.963 921.618 928.372 946.639 958.242]
22 deg: [ {\color{green}850.134} 901.281 910.963 920.6 958.242]

>>>>

\begin{table}
    \begin{center}
      \caption{Wavelength at which peaks happen for different aspect ratios, for runs where the electric
      field is parallel to the length (L) of the pillar. We have normal incidence and 22 degrees.}
      \label{tab:table1}
      \begin{tabular}{c c c c c c c c}
        \textbf{AR} \\
        \hline
        \multirow{2}{*}{1} & $\perp$ & \textbf{917.73} & 934.092 & 949.604 & 957.325 \\ % <-- Combining 2 rows with arbitrary with (*) and content 12
        & 22$^{\circ}$ & 883.926 & \textbf{917.73} & 935.052 & 949.604 & 957.325 \\ % <-- Content of first column omitted.
        \hline
        \multirow{2}{*}{2} & $\perp$ & \textbf{903.233} & 926.395 & 944.762 & 958.242 \\ % <-- Combining 2 rows with arbitrary with (*) and content 12
        & 22$^{\circ}$ & 896.517 & \textbf{903.233} & 926.395 & 944.762 & 958.242 \\ % <-- Content of first column omitted.
        \hline
        \multirow{2}{*}{3} & $\perp$ & \textbf{888.793} & 922.552 & 931.223 & 948.613 & 958.242 \\ % <-- Combining 2 rows with arbitrary with (*) and content 12
        & 22$^{\circ}$ & \textbf{888.793} & 899.418 & 922.552 & 931.223 & 958.242 \\ % <-- Content of first column omitted.
        \hline
        \multirow{2}{*}{4} & $\perp$ & \textbf{876.186} & 929.32 & 946.639 & 958.242 \\ % <-- Combining 2 rows with arbitrary with (*) and content 12
        & 22$^{\circ}$ & \textbf{876.186} & 901.281 & 921.618 & 929.32 & 945.745 & 958.242 \\ % <-- Content of first column omitted.
        \hline
        \multirow{2}{*}{5} & $\perp$ & \textbf{865.576} & 926.395 & 945.745 & 958.242 \\ % <-- Combining 2 rows with arbitrary with (*) and content 12
        & 22$^{\circ}$ & \textbf{865.576} & 901.281 & 921.618 & 958.242 \\ % <-- Content of first column omitted.
        \hline
        \multirow{2}{*}{6} & $\perp$ &  \textbf{856.904} & 914.793 & 923.489 & 929.32 & 946.639 & 958.242\\ % <-- Combining 2 rows with arbitrary with (*) and content 12
        & 22$^{\circ}$ & \textbf{856.904} & 901.281 & 920.6 & 958.242\\ % <-- Content of first column omitted.
        \hline
        \multirow{2}{*}{7} & $\perp$ &  \textbf{850.134} & 910.963 & 921.618 & 928.372 & 946.639 & 958.242 \\ % <-- Combining 2 rows with arbitrary with (*) and content 12
        & 22$^{\circ}$ & \textbf{850.134} & 901.281 & 910.963 & 920.6 & 958.242\\ % <-- Content of first column omitted.
        \hline

      \end{tabular}
    \end{center}
  \end{table}
